\CO observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with continuum detection in the lensing FR-II galaxy 3C220.3

### 2015-06-28 skeleton.tex
Up to dyn mass

%\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
\usepackage{amsmath}
\usepackage{natbib}
\citestyle{aa}
\shorttitle{Study of a strongly lensed type-2 quasar host SMG at $z$ = 2.221}
%\shortauthors{Leung and Riechers}

\begin{document}
\title{\CO observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with
continuum detection in the lensing FR-II galaxy 3C220.3}
\author{No name}
%\author{T. K. Daisy Leung\altaffilmark{1} and Dominik R. Riechers}
%\affil{Astronomy Department, Cornell Unviersity}
%\altaffiltext{1}{tleung@astro.cornell.edu}

\begin{abstract}
We report the detection of \CO line emission in SMM J0939+8315 ($z$ = 2.221), a
strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
foreground radio galaxy and a companion galaxy at $z$ = 0.685. A lensing magnification of $\mu_{\rm 1 mm}$ = 9.74 $\pm$ 1.4 amplified the intrinsic luminosities of the CO emission. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing 
amplification, we measure the
velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s\pmOne,
corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (4.1 $\pm$ 
0.9) $\times$ 10$^{10}$ \LpU. This
translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$, assuming a conversion
factor of $\alpha_{\rm CO}$ = 0.8 \Msun (\LpU)\pmOne. We report marginally resolved continuum 
emission from the foreground radio galaxy 3C220.3 with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz, allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG using existing
infrared photometric data. Our SED fitting favours an optically thick model, yielding dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8$\Msun, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
_{-2.6}\times$10$^{12}$\Lsun, prior to lensing correction. We conclude that the properties (\eg gas mass, gas mass 
fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio.. Comparison, etc. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

@@

In this paper, we present the detection of \CO line emission obtained with the Combined
Array for Research in Millimeter Astronomy (CARMA) in the background SMG
SMM J0939 at $z$ = 2.221. The underlying radio continuum at 104 GHz allows us to put constraints on the SED of the 
foreground radio galaxy. This paper is organized as follows: in \S \ref{sec:obs}, we describe the
observations of the \CO line emission with CARMA; in \S \ref{sec:res}, we report the
detection of the CO line in the background galaxy as well as the continuum in the foreground galaxy; in \S
\ref{sec:Lens}, we present our lens modeling analysis; in \S \ref{sec:SED}, we perform SED fitting to 3C220.3
and SMM J0939 and derive the intrinsic properties of the interstellar medium (ISM) in the SMG; in \S \ref{sec:conclusions}, we
conclude our findings by comparing to other SMGs at similar redshifts.

@@

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens} 
To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
lens modeling using the SMA 1 mm archival data of this system. The lens modeling is carried out in the visibility
(uv-) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}
\citep{Bussmann15a}. The code uses affine-invariant Markov chain Monte Carlo (MCMC) to sample the posterior
probability density function (PDF) of the model parameters. In our lens model, the surface mass densities of both
lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
elliptical Gaussian profile. The code does not include an external shear parameter. \newline
We fix the phase center to coordinates ($\alpha$, $\delta$) (J2000) = (144.84809\degr, 83.25725\degr), the
offset positions of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
described by 5 free parameters: the angular offset relative to
the chosen phase center in the image ($\Delta \alpha_{\rm
lens0}$ and $\Delta \delta_{\rm lens0}$), the angular Einstein radius ($\theta_{\rm E,0}$), the
axial ratio ($q_{\rm lens0}$), and the position angle ($\phi_{\rm lens0}$). The secondary lens (companion B) is
described by 3 free parameters: $\theta_{\rm E,1}$, $q_{\rm lens1}$, and $\phi_{\rm lens1}$. The angular offset
of the secondary
lens is sampled with respect to ($\Delta \alpha_{\rm lens0}$ and $\Delta \delta_{\rm lens0}$) of
the primary lens.
The source (SMM J0939) is parameterized by
6 free parameters: the position of the source relative to the
primary lens ($\Delta \alpha_{\rm s}$ and $\Delta
\delta_{\rm s}$), the total intrinsic flux density ($S$), the
effective radius ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm s}}$), the axial
ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position angle
($\phi_{\rm s}$).
The total number of free parameters is $N_{\rm free}$ = 14. The best-fit model is obtained by maximizing the
Gaussian likelihood function $ \mathcal{L} $ according to:
\begin{equation}
    \mathcal{L} = \sum_{u, v}\left( \frac{|V_{\rm data} - V_{\rm
    model}|^2}{\sigma^2} + {\rm log}(2 \pi \sigma^2) \right)
\end{equation}
\noindent where $\sigma$ is determined from the scatter in the visibilities within a
single spectral window (natural weighting).

@@

The resulting best-fit model as shown in Figure \ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
The best-fit model yields a magnification
factor of $\mu_{\rm 1mm}$ = 9.73 $\pm$ 1.38, this is consistent the value reported by \citet{Haas14} within errors. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.73 $\pm$ 0.02 (5.23 kpc at $z$ = 0.685),
the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
\Msun 
and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ \Msun, respectively. All best-fit
parameters are listed in Table \ref{tab:lensParam}.
\input{table_lensParams}

\subsection{SED fitting} \label{sec:SED}
\subsubsection{3C220.3}
In the theory of synchrotron emission, continuum emission from extended components of a radio galaxy decreases with increasing frequencies, and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$ where the spectral index $\alpha$ is $\gtrsim$ 0.5. While the contribution from extended components decreases, studies using samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises and dominates the flux density at higher frequencies (cite). Consequently, we expect the peak flux density in our continuum detection of $S_{\rm 104GHz}$ = 5.56 $\pm$ 0.54 mJy to be dominated by the unresolved core component of the foreground FR-II. On the other hand, the integrated flux density of 7.18 $\pm$ 0.69 mJy is suggestive of a marginally resolved detection of the extended components with non-negligible emission. This is plausible given that the orientation of the synthesized beam in our observations aligns with the axis along the 
lobes of the radio galaxy, as shown in Figure \ref{fig:cont}. We investigate this disparity by fitting an SED to existing data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to estimate the flux density of the lobes at the frequency of our continuum measurement. For the core, an upper limit of $<$0.17 mJy at 4.6 GHz \citep{Mullin06a}, and a clear detection of 0.8 mJy at 9 GHz (H14) is indicative of a substantially inverted spectrum of the core, although we note that these measurements are taken across epochs. All measurements are plotted in Figure \ref{fig:SED}. \input{table_SED}
Following Equation (1) in \citet{Cleary07a}, the fit to the lobes can be expressed as a parabolic function:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution.

@@

\input{table_mbb}
The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in appendix. The best-fit solution of an optically thin
model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than the optically thin
model. In the subsequent analysis, we employ the inferred values from the optically thick model.
The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.33$^{+1.14}_{-1.13}\times$10$^{12}$\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.52$^{+2.62}_{-2.63}\times$10$
^{12}$\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64 m$^2$ kg\pmOne at 125.0 $
\micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
\begin{equation}
M_{\rm dust} = S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
\exp(-\tau_{\nu})]^{-1}
\end{equation}
where $S_{\nu}$ is the flux density, $D_{\rm L}$ is the luminosity distance, $\kappa_{\nu}$ is the dust
absorption coefficient, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
all quantities are expressed in the observed-frame. We find a dust mass of $M_{\rm dust}$ =
50.47$^{20.42}_{-20.15}\times$10$^8$\Msun, the uncertainties do not include those of $\kappa_{\nu}$. These values are based on SED fitting to the photometric data, i.e. prior
to lensing correction.
With the limited amount of data in the FIR, $M_{\rm dust}$ is weakly constrained; in another optically thick model where the upper limit of $\beta$ is set to 3.0, all fitting parameters of the best-fit solution is similar to those using an upper limit of 2.2, vary at most blah\% except for $\lambda_0$, which blah blah, the dust mass is boosted by a factor of $\sim$2.

\subsection{Molecular gas mass}
The ground state CO transition line, CO($J$ = 1 \rarr 0) has been used as a tracer of the cold molecular gas in galaxies for over a decade. For high-redshift galaxies, the CO(J$>$1) transition lines are  
, assumptions on the CO excitation conditions is required to derive the molecular gas mass using the H2 to CO relation.

It has long been assumed that the molecular gas in the ISM of SMGs traced by CO is thermalized given their high star formation rates (e.g. Greve et al. 2005; Coppin et al. 2008; Tacconi et al. 2008). With the few SMGs with CO(1-0) and higher J co observations to date,
Recent CO(1-0) observations of SMGs have demonstrated that SMGs can indeed be subthermally excited. (Bothwell et al. 2013, Harris et al. (2010). In these galaxies with subthermal excitation at the (3-2) transition, the brightness temperature ratio between CO(3-2) and CO(1-0) is $<$ 0.8. with an average radio of R31 = 0.6 pm 0.1 \citep[\eg][]{Harris10a,Carilli10a,Swinbank2010a,Ivison11a,Ivison10d}. While these brightness temperature ratios are $\sim$0.6 in SMGs, observations of high-z quasars suggest that the host galaxies have ratios close to unity (e.g., Riechers 
et al. 2006; 2011a; Ivison et al. 2012). Since only \CO line has been detected on this object, we adopt 1 here since the source is hosting a quasar.

We derive the molecular gas mass in
this SMG assuming thermalized excitation of CO, i.e. the brightness temperature ratio 
between \CO
and ($J$ = 1 \rarr 0) is $R_{31}$ = 1 \citep[\eg][and references therein]{Riechers11a,Scott11a}
%(\eg Ivison et al. 2008, 2012). 
We calculate the CO($J$ = 1 \rarr 0) line luminosity using standard relations 
\citep[\eg][]{Solomon05a,Carilli13a}:
\begin{equation}
L^{\prime}_{\rm CO} = \frac{3.25\times10^7}{\nu_{\rm CO (3-2), rest}^2}\times \frac{D_L^2}{\mu} \times
\frac{I_{\rm CO(3-2)}} {R_{\rm 31} (1 + z)}
\end{equation}
this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ \pmOne (\rm K km s
\pmOne pc$^2$)
after lensing correction. The inferred total molecular gas mass is therefore M$_{\rm gas}$ = (3.3$\pm$0.7) $\times
$10$^{10}$ ($\alpha$/0.8) \Msun. We assumed a conversion factor of $\alpha_{\rm CO}$ =
0.8 \Msun (\LpU)\pmOne based on empirical relations from local ULIRGs, which is typically
adopted for SMGs \citep{Bothwell13a,Tacconi10a,Daddi2010a}. 
Combining with the dust mass derived from SED fitting, the gas-to-dust
ratio is $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , which is in good agreement with the range 
of values found in other SMGs \citep{Coppin08a}.

% ~ 120 for MW (Coppin 2007)
% ~ 60 for typical SMG (coppin 2008)
% ~ 100 for LBG (coppin 2007)

\subsection{Star formation rate}
We derive the star formation rate (SFR) using the \citet{Kennicutt98a} relation, assuming a \citet{Chabrier03a}
stellar initial mass (IMF) function: SFR = 1.0 $\times$ 10$^{-10}\times$ ($L_{\rm IR\ or\ FIR}$). This yields SFR$_{\rm IR}$ 
= (909.12 $\pm$ 155.67) $\times\ (\mu/9.74)^{-1}$ [$M\sun$ yr\pmOne] and SFR$_{\rm FIR}$ (547.71 $\pm$ 89.28) $\times(\mu/9.74)^{-1}$ [M$
\sun$ yr\pmOne] using lensing-corrected (far-)infrared luminosities (L$_{\rm IR}$ and L$_{\rm FIR}$) derived from our SED 
fitting, and assuming negligible contributions from AGN heating.

Assuming constant SFR, the minimum time for which the starburst in SMM J0939 can be maintained at its
current SFR is approximated by the gas depletion timescale $\tau$ = $M_{\rm gas}$/SFR, which is $\tau_{\rm IR}$ = 36.33$\pm$ blah 
Myr, and $\tau_{\rm FIR}$ = 60.30$\pm$blah Myr.

Move to discussion: Compare THIS NUMBER: with other SMGs (\eg \citep{Greve05a}).

\subsection{SFE}
The SFR per unit mass of molecular gas is commonly taken as a
measure of the star formation efficiency, SFE = SFR/$M_{\rm gas}$. We compute the ratio using lensing-corrected (far-)infrared 
luminosities ($L_{\rm IR}$ or $L_{\rm FIR}$) and CO($J$ = 1 \rarr 0) luminosity SFE = $L_{\rm F/IR}$/\Lp, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ and is independent of the 
choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible.

We find a ratio of SFE$_{\rm IR}$ = 220.22 Myr\pmOne and SFE$_{\rm FIR}$ = 132.68 Myr\pmOne, which are comparable
to what is found in "typical" SMGs (tacconi et al. 2006, Riechers et al. 2010, cite).
Greve 05.

\subsection{Dynamical mass} %% check half light radius error, and comparison
We derive the dynamical mass of SMM J0939 using an isotropic virial estimator \citep[\eg][]{Engel10a}:
\begin{equation}
M_{\rm dyn} = 2.8\times 10^5\Delta \rm v_{\rm line}^ 2 R_{\rm eff}
\end{equation}
where the line width $\Delta \rm v_{\rm line}^ 2$ is based on our \CO line
measurement and $R_{\rm eff}$ is approximated with the half-light radius of the best-fit lens model. This yields $M_{\rm dyn}$ = blah, and gas-to-
dynamical mass fraction of $f_{\rm gas-to-dyn}$ = 2.03.

@@

A lensed SMG that is likely to be hosting a type-2 quasar, this source offers an exceptional opportunity to
investigate the gas mass and dynamics of this
poorly-studied population of high z galaxies.

>>>>

%\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
\usepackage{amsmath}
\usepackage{natbib}
\citestyle{aa}
\shorttitle{Study of a strongly lensed type-2 quasar host SMG at $z$ = 2.221}
\shortauthors{Leung \& Riechers}

\begin{document}
\title{\CO observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with
continuum detection in the lensing FR-II galaxy 3C220.3}
\author{T. K. Daisy Leung\altaffilmark{1} and Dominik R. Riechers}
\affil{Astronomy Department, Cornell Unviersity}
\altaffiltext{1}{tleung@astro.cornell.edu}

\begin{abstract}
We report the detection of \CO line emission in SMM J0939+8315 at $z$ = 2.221, a
strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
foreground radio galaxy 3C220.3 and a companion galaxy at $z$ = 0.685. A lensing magnification of $\mu_{\rm 1 mm}$ = 9.74 $\pm$ 1.4 amplified the intrinsic luminosities of the CO emission. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing 
amplification, we measure the
velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s\pmOne,
corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (4.1 $\pm$ 
0.9) $\times$ 10$^{10}$ \LpU. This
translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$. We report marginally resolved continuum 
emission from the foreground galaxy with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz, allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG, the preferable optically thick model  yields dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8$\Msun, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
_{-2.6}\times$10$^{12}$\Lsun, prior to lensing correction. We conclude that the properties (\eg gas mass, gas mass 
fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio.. Comparison, etc. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

@@

In this paper, we present the detection of \CO line emission obtained with the Combined
Array for Research in Millimeter Astronomy (CARMA) in the background SMG
SMM J0939 at $z$ = 2.221. The underlying radio continuum at 104 GHz allows us to put constraints on the SED of the 
foreground radio galaxy.

This paper is organized as follows: in \S \ref{sec:obs}, we describe the
observations of the \CO line emission with CARMA; in \S \ref{sec:res}, we report the
detection of the CO line in the background galaxy as well as the continuum in the foreground galaxy; in \S
\ref{sec:Lens}, we present our lens modeling analysis; in \S \ref{sec:SED}, we perform SED fitting to 3C220.3
and SMM J0939 and derive the intrinsic properties of the interstellar medium (ISM) in the SMG; in \S \ref{sec:conclusions}, we
conclude our findings by comparing to other SMGs at similar redshifts.

@@

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens} 
To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
lens modeling using the SMA 1 mm archival data of this system. The lens modeling is carried out in the visibility
(uv-) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}
\citep{Bussmann15a}. The code uses affine-invariant Markov chain Monte Carlo (MCMC) to sample the posterior
probability density function (PDF) of the model parameters. In our lens model, the surface mass densities of both
lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
elliptical Gaussian profile. The code does not include an external shear parameter.

We fix the phase center to coordinates ($\alpha$, $\delta$) (J2000) = (144.84809\degr, 83.25725\degr), the
offset positions of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
described by 5 free parameters: the angular offset relative to
the chosen phase center in the image ($\Delta \alpha_{\rm
lens0}$ and $\Delta \delta_{\rm lens0}$), the angular Einstein radius ($\theta_{\rm E,0}$), the
axial ratio ($q_{\rm lens0}$), and the position angle ($\phi_{\rm lens0}$). The secondary lens (companion B) is
described by 3 free parameters: $\theta_{\rm E,1}$, $q_{\rm lens1}$, and $\phi_{\rm lens1}$. The angular offset
of the secondary
lens is sampled with respect to ($\Delta \alpha_{\rm lens0}$ and $\Delta \delta_{\rm lens0}$) of
the primary lens.
The source (SMM J0939) is parameterized by
6 free parameters: the position of the source relative to the
primary lens ($\Delta \alpha_{\rm s}$ and $\Delta
\delta_{\rm s}$), the total intrinsic flux density ($S$), the
effective radius ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm s}}$), the axial
ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position angle
($\phi_{\rm s}$).
The total number of free parameters is $N_{\rm free}$ = 14. The best-fit model is obtained by maximizing the
Gaussian likelihood function $ \mathcal{L} $ according to:
\begin{equation}
    \mathcal{L} = \sum_{u, v}\left( \frac{|V_{\rm data} - V_{\rm
    model}|^2}{\sigma^2} + {\rm log}(2 \pi \sigma^2) \right)
\end{equation}
\noindent where $\sigma$ is determined from the scatter in the visibilities within a
single spectral window (natural weighting).

@@

The resulting best-fit model as shown in Figure \ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
The best-fit model yields a magnification
factor of $\mu_{\rm 1mm}$ = 9.73 $\pm$ 1.38, this is consistent the value reported by \citet{Haas14} within errors. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.73 $\pm$ 0.02 (5.23 kpc at $z$ = 0.685),
the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
\Msun\ 
and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ \Msun, respectively. All best-fit
parameters are listed in Table \ref{tab:lensParam}.
\input{table_lensParams}

\subsection{SED fitting} \label{sec:SED}
\subsubsection{3C220.3}
In the theory of synchrotron emission, continuum emission from extended components of a radio galaxy decreases with increasing frequencies, and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$ where the spectral index $\alpha$ is $\gtrsim$ 0.5. While the contribution from extended components decreases, studies using samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises and dominates the flux density at higher frequencies (cite). Consequently, we expect the peak flux density in our continuum detection of $S_{\rm 104GHz}$ = 5.56 $\pm$ 0.54 mJy to be dominated by the unresolved core component of the foreground FR-II. On the other hand, the integrated flux density of 7.18 $\pm$ 0.69 mJy is suggestive of a marginally resolved detection of the extended components with non-negligible emission. This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the axis along the 
lobes of the radio galaxy, as shown in Figure \ref{fig:cont}. We investigate this disparity by fitting an SED to existing data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to estimate the flux density of the lobes at the frequency of our continuum measurement. For the core, an upper limit of $<$0.17 mJy at 4.6 GHz \citep{Mullin06a}, and a clear detection of 0.8 mJy at 9 GHz (H14) is indicative of a substantially inverted spectrum of the core, although we note that these measurements are taken across epochs. All measurements are plotted in Figure \ref{fig:SED}. \input{table_SED}
Following Equation (1) in \citet{Cleary07a}, the fit to the lobes can be expressed as a parabolic function:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution.

@@

\input{table_mbb}
The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in appendix. The best-fit solution of an optically thin
model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than the optically thin
model. In the subsequent analysis, we employ the inferred values from the optically thick model.
The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.33$^{+1.14}_{-1.13}\times$10$^{12}$\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.52$^{+2.62}_{-2.63}\times$10$
^{12}$\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64 m$^2$ kg\pmOne at 125.0 $
\micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
\begin{equation}
M_{\rm dust} = S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
\exp(-\tau_{\nu})]^{-1}
\end{equation}
where $S_{\nu}$ is the flux density, $D_{\rm L}$ is the luminosity distance, $\kappa_{\nu}$ is the dust
absorption coefficient, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
all quantities are expressed in the observed-frame. We find a dust mass of $M_{\rm dust}$ =
50.47$^{20.42}_{-20.15}\times$10$^8$\Msun, the uncertainties do not include those of $\kappa_{\nu}$. These values are based on SED fitting to the photometric data, i.e. prior
to lensing correction. With the limited amount of data in the FIR, $M_{\rm dust}$ is weakly constrained; in another fit to the optically thick model where the upper limit of $\beta$ is set to 3.0, all fitting parameters of the best-fit solution are similar to those using an upper limit of 2.2, we find that the deviation of each is at most $\sim$3\% whereas the dust mass is boosted by a factor of $\sim$2.

\subsection{Molecular gas mass}
The ground state CO transition line, CO($J$ = 1 \rarr\ 0) has been used as a tracer of the cold molecular gas in galaxies for 
over a decade \citep*[\eg][]{Downes98a}. For high-redshift galaxies, the CO($J$ $>$ 1) transition lines are frequently observed as
 the CO($J$ = 1 \rarr\ 0) line is redshifted to wavelengths that can only be observed with a few telescopes \citep{Carilli13a}, 
 hence assumptions on the CO excitation conditions are required to derive the molecular gas mass using the H$_{\rm 2}$-to-CO 
 relation. Prior to the observations of the CO($J$ = 1 \rarr\ 0) line in SMGs, it has been assumed that the molecular gas in the
  ISM traced by CO transition lines is thermalized due to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
   Nonetheless, recent CO($J$ = 1 \rarr\ 0) observations have demonstrated that SMGs can indeed be subthermally excited
   \citep{Bothwell13a, Harris10a}. Based on SMGs with observations of both the \CO and the CO($J$ = 1 \rarr\ 0) lines, the 
   brightness temperature ratio between \CO
and ($J$ = 1 \rarr\ 0) has been inferred as $R_{\rm 31}<$ 0.8 \citep
   {Harris10a,Carilli10a,Swinbank2010a,Ivison11a,Ivison10d}. In contrast, observations of high-redshift quasar hosts suggest that the ratio 
   is $\sim$1 \citep{Riechers06a, Riechers11a, Scott11a}. 
Here, we derive the molecular gas mass assuming thermalized excitation of CO, i.e., we adopt $R_{\rm 31}$ = 1 as SMM J0939 is 
postulated to be hosting a quasar. We calculate the CO($J$ = 1 \rarr\ 0) line luminosity using standard relation 
\citep[\eg][]{Solomon05a,Carilli13a}:
\begin{equation}
L^{\prime}_{\rm CO} = \frac{3.25\times10^7}{\nu_{\rm CO (3-2), rest}^2}\times \frac{D_L^2}{\mu} \times
\frac{I_{\rm CO(3-2)}} {R_{\rm 31} (1 + z)}
\end{equation}
this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ \LpU after lensing correction. The inferred total molecular gas mass is therefore $M_{\rm gas}$ = (3.3 $\pm$ 0.9) $\times
$10$^{10}$ \Msun. We assumed a conversion factor of $\alpha_{\rm CO}$ =
0.8 \Msun (\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
adopted for SMGs \citep[\eg][]{Bothwell13a,Tacconi10a,Daddi2010a}. 
The gas-to-dust
ratio is $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , this is in good agreement with the range 
of values found in other SMGs \citep{Coppin08a}.

\subsection{Star formation rate}
We derive the star formation rate (SFR) using the \citet{Kennicutt98a} relation, assuming a \citet{Chabrier03a}
stellar initial mass (IMF) function. This yields SFR$_{\rm IR}$ 
= 909.12 $\pm$ 155.67 $M\sun$ yr\pmOne and SFR$_{\rm FIR}$ = 547.71 $\pm$ 89.28 $M
\sun$ yr\pmOne\ using lensing-corrected (far-)infrared luminosities (L$_{\rm IR}$ and L$_{\rm FIR}$) derived from SED 
fitting, and assuming negligible contributions from AGN heating.

Assuming constant SFR, the minimum time for which the starburst in SMM J0939 can be maintained at its
current SFR can be approximated as the gas depletion timescale, $\tau$ = $M_{\rm gas}$/SFR. 
This corresponds to $\tau_{\rm IR}$ = 36.33 $\pm$ blah Myr, and $\tau_{\rm FIR}$ = 60.30 $\pm$ blah Myr.

Move to discussion: Compare THIS NUMBER: with other SMGs \citep[\eg][]{Greve05a}.

\subsection{star formation efficiency}
The SFR per unit mass of molecular gas is commonly taken as a
measure of the star formation efficiency, SFE = SFR/$M_{\rm gas}$. We compute this ratio using lensing-corrected (far-)infrared 
luminosities ($L_{\rm IR}$, $L_{\rm FIR}$) and CO($J$ = 1 \rarr\ 0) luminosity: SFE = $L_{\rm F/IR}$/\Lp, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ as well as the 
choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible. 
The resulting ratios are SFE$_{\rm IR}$ = 220.22 $\pm$ blah Myr\pmOne\ and SFE$_{\rm FIR}$ = 132.68 $\pm$ blah Myr\pmOne, which are comparable
to what is found in "typical" SMGs \citep{Riechers10, Tacconi06, Greve05a}.

\subsection{Dynamical mass} 
We derive the dynamical mass of SMM J0939 using an isotropic virial estimator \citep[\eg][]{Engel10a}:
\begin{equation}
M_{\rm dyn} = 2.8\times 10^5\Delta v_{\rm line}^ 2 R_{\rm eff}
\end{equation}
where we employ the FWHM line width of our \CO measurement for $\Delta v_{\rm line}$,
and the half-light radius from lens modeling for $R_{\rm eff}$, assuming the dust emission traces the same emitting region as the CO. This yields $M_{\rm dyn}$ = blah, and gas-to-dynamical mass fraction of $f_{\rm gas-to-dyn}$ = BLAH2.03.

@@

This paper focuses on a blah source J0939+8315, a lensed SMG that is likely to be hosting a type-2 quasar, this source offers an exceptional opportunity to
investigate the gas mass and dynamics of this
poorly-studied population of high z galaxies.

In this paper, we present blah of a strongly lensed blah at z = 2.221, at the epoch of cosmic star formation (cite)

We report a detection of \CO line.
The continuum detection is marginally resolved, we place constraints on the SED of the foreground galaxy (accounting for radio 
core and lobes emission). Our CO measurement confirms the redshift of this source, which was previously measured using CIV and HeII lines (H14).
